\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan
}
\geometry{
    a4paper,
    left=0.5cm,
    right=0.5cm,
    top=0.2cm,
    bottom=0.5cm
}

\usepackage{amsmath}
\usepackage[most]{tcolorbox}

\begin{document}

% making the title
\begin{tcolorbox}[colback=blue!5!white,colframe=blue!5!white, arc=0mm]
\begin{center}
\textbf{\Huge Izaac Laundry Mottiar} \\
\vspace{0.15cm}
\text{\LARGE 3A Mechatronics Engineering University of Waterloo} \\
\vspace{0.15cm}
\text{ 905-341-0341 \hspace{3.5cm} imlaundr@uwaterloo.ca \hspace{3.5cm} \href{https://www.linkedin.com/in/izaac-mottiar/}{LinkedIn}}
\end{center}
\end{tcolorbox}

%Projects
\vspace{0.3cm}
\text{ I'm currently in my third year of Mechatronics Engineering at the University of Waterloo, specializing in embedded}

\text{ systems and software development. Feel free to explore my \href{https://izaac08.github.io/Portfolio/}{portfolio} to learn more about the projects I've worked on.}

%Techinal Section

% \vspace{-0.3cm}
\section*{\hspace{0.2cm} \large Technical Skills}
\begin{center}
    \vspace{-0.5cm}
    \rule{\textwidth}{0.1pt}
\end{center}

\begin{description}
    \vspace{-0.5cm}
     \item[\hspace{0.5cm}Programming:] Fluent in Python, C/C++, MATLAB, MS Excel, Ladder Logic, JavaScript and CSS.
    \vspace{-0.2cm}
    \item[\hspace{0.5cm}Mechanical:] Skilled in AutoCAD, SolidWorks, and Fusion 360, with experience in 3D Printing and Machining
    \vspace{-0.2cm}
    \item[\hspace{0.5cm}Electrical:] Experienced in circuit and PCB design, leveraging STM32, Arduino, and Raspberry Pi platforms.
\end{description}


%Experience Section
\vspace{-0.5cm}     
\section*{\hspace{0.2cm} \large Work Experience}
\begin{center}
    \vspace{-0.5cm}
    \rule{\textwidth}{0.1pt}
\end{center}

%Firmware Team Member - UW Robotics Team
\vspace{0cm}
\textbf{\hspace{-0.10cm} UW Robotics Team} | Firmware Team Member, Waterloo ON. \hspace {4.5cm} {\small Jan. 2025 - April. 2025}

\vspace{-0.2cm}
\begin{itemize}[leftmargin=1.5cm]

    \item {Implemented SPI communication between STM32 and ERCK 05SPI 360 encoder.
    \vspace{-0.2cm}
    \begin{itemize} [label=$\circ$, leftmargin=0.5cm]
        \item {Utilized logic analyzer to capture and debug digital signal traces.}
    \end{itemize}
    
    }    
\end{itemize}



%Standard BioTools
\vspace{0cm}
\textbf{\hspace{-0.10cm} Hardware Test Intern} | StandardBioTools, Markham ON. \hspace {5.2cm} {\small Sept. 2024 - Dec. 2024}

\vspace{-0.2cm}
\begin{itemize}[leftmargin=1.5cm]

    \item {Conducted lifecycle testing by integrating a pneumatic actuator and camera system to automate physical testing \\ and validate results.
    \vspace{-0.2cm}
    \begin{itemize} [label=$\circ$, leftmargin=0.5cm]
        \item {Developed a script to manage the process, ensuring autonomous operation and automated result collection.}
    \end{itemize}
    }


    \vspace{-0.2cm}
    \item Analyzed and certified five gas manifolds by performing leak checks, pressure sensor accuracy tests, and MFC \\ precision and resolution analysis.
    \vspace{-0.2cm}
    \begin{itemize} [label=$\circ$, leftmargin=0.5cm]
        \item Authored Project Change Requests to address design issues and improve designs.
        \item Led supplier meetings to resolve MFC inconsistencies and streamline communication.
        \item Developed Python scripts to automate data collection for pressure sensors, flow rates, and leak detection.

    \end{itemize}
        
    

    
\end{itemize}


\textbf{\hspace{-0.10cm} Manufacturing Engineering Intern} | Greenhouse Juice Co. Mississauga ON. \hspace{2.2cm} {\small Jan. 2024 - April. 2024}

\vspace{-0.2cm}
\begin{itemize}[leftmargin=1.5cm]
    %need to reword the 
    \item Integrated the NIMCO Gable Top machine into production, increasing juice production by 10\%.
    \vspace{-0.2cm}
    \begin{itemize} [label=$\circ$, leftmargin=0.5cm]
        \item Engineered custom jigs and developed UV monitoring protocols for precise liquid flow control.
        \item Created an SOP and trained operators for consistent implementation.
        
    \end{itemize}

    \vspace{-0.1cm}
    \item Developed a hydrogen peroxide detection system using OAK-1 PoE and Raspberry Pi 5, enabling real-time \\ monitoring, LED updates, and automated Excel logging.

    \vspace{-0.1cm}
    \item Monitored machinery data, performed daily water titration tests, and tracked gas, water, and electricity consumption \\ to optimize resource usage.
    
\end{itemize}

\textbf{\hspace{-0.10cm} Controls Specialist Intern} | JMP Solutions, Oakville ON. \hspace{5.3cm} {\small May. 2023 - Sept. 2023}

\vspace{-0.2cm}
\begin{itemize}[leftmargin=1.5cm]
    \item Developed and programmed PLCs to regulate the drive speed of two KOBM slurry pumps for ArcelorMittal \\ Dofasco, optimizing operational efficiency.

    \vspace{-0.1cm}

    \item Collaborated closely with the Vice President and General Manager of Integration and Engineering Services to \\ successfully complete a corporate-wide file management initiative.

    \vspace{-0.1cm}

    \item Drafted nine x-axis motion and nine z-axis motion drives to control multi-cut saws used for cutting exhaust pipes \\ of varying lengths for ArcelorMittal Dofasco.

\end{itemize}

%Chassis Team Member
% \textbf{\hspace{-0.10cm} Chassis Team Member} | University of Waterloo Formula Motorsports \hspace{3.3cm} {\small Sept. 2023 - April. 2023}

% \vspace{-0.2cm}
% \begin{itemize}[leftmargin=1.5cm]
%     \item Crafted an aluminum hose valve on the lathe and precision-milled various brackets.


%     \vspace{-0.1cm}

%     \item Designed and fabricated a cover for the radiator using SolidWorks and waterjet cutting techniques.
% \end{itemize}



%Education Section
\vspace{-0.5cm}
\section*{\hspace{0.4cm} \large Education}
\begin{center}
    \vspace{-0.5cm}
    \rule{\textwidth}{0.1pt}
\end{center}


\begin{description}
    \vspace{-0.5cm}
    \item[\hspace{0.6cm}University of Waterloo] | Candidate for Bachelors of Mechatronics Engineering. \hspace{2.3cm} {\small Sept. 2022 - Present}
    \vspace{-0.2cm}
    \item[\hspace{0.6cm}Secondary School ] | Graduated with honours diploma and 98\% average \hspace{3.1cm} {\small Sept. 2018 - June. 2022}
\end{description}



%Interest Section
% \vspace{-0.5cm}     
\vspace{0.5cm}
% \section*{\hspace{0.4cm} \large Interests}
% \begin{center}
%     \vspace{-0.5cm}
%     \rule{\textwidth}{0.1pt}


    \text{Outside of my professional pursuits, I am actively engaged in various university intramural sports, including soccer,}
    
    \text{basketball, and tennis. I also enjoy a wide range of other physical activities such as bouldering, racing, and backpacking.}
    
    \text{When time permits, I unwind by reading, playing video games, and on the off occasion, hanging out with my girlfriend.}

\end{document}
